\mytitile\\~

### 2019-11-26 document.tex
Changing in appendix D

\begin{equation}
A^{(2)}_{1\rightarrow 6} =\pi\Omega_2^4 \frac{16 J^4 \left(3 \alpha_2 ^2+7 \text{$\Omega_1
		$}^2\right)^2}{\alpha_2 ^{10}}
\end{equation}
\begin{equation}
A^{(2)}_{2\rightarrow 5} =\pi\Omega_2^4 \frac{4 J^4 (5 \alpha_2 +3 \text{$\Omega_1$})^2}{\alpha_2 ^8}
\end{equation}
From here it follows that in the studied SAM the sideband transitions are prohibited without interaction $(J=0)$ even in the second order, and the avoided crossing we are interested can not be observed.

@@

Solving \autoref{forpsi} by simple iteration gives the series solution
\begin{equation}
	U(t,t_0) = 1+\sum_{n}U^{(n)}(t,t_0)
\end{equation}
\begin{equation}
	U^{(n)}(t,t_0) = -i^n \int_{t_0}^{t}d t_1\tilde{V}(t_1)...\int_{t_0}^{t_{n-1}}d t_n\tilde{V}(t_n)
\end{equation}
For "weak" interaction the series may be truncated to a fine term $n$ and the $n$th- order transition amplitude $\bra{f}U^{(n)}(t,t_0)\ket{i}$ can be evaluated. 
In our case the interaction in interaction picture satisfies the following relation
\begin{equation}
	\begin{split}
	\tilde{V}(t)=\exp(i H_0 t) \Omega\cos(\omega_d t)(\hat b+\hat b^{\dagger})\exp(-i H_0 t)\overset{RWA}{=}\\ \exp(i H_0 t) \Omega(\hat b^{\dagger} e^{-i\omega_d t}+\hat be^{i\omega_d t})\exp(-i H_0 t)
	\end{split}
\end{equation}
Taking the matrix element between the initial and the final states $\ket{i}$ and $\ket{f}$, one immediately obtains
\begin{equation}
	\begin{split}
	\bra{f}U^{(1)}(t,t_0)\ket{i}=-i\int_{t_0}^{t}dt_1\tilde{V}(t_1)=\\-i\frac{\Omega}{2}\big[\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i-\omega_d)t_1}\bra{f}b^{\dagger}\ket{i}+\\
	\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i+\omega_d)t_1}\bra{f}b\ket{i}\big]
	\end{split}
\end{equation}
To calculate second-order term we used the following expression $\sum_{j}\ket{j}\bra{j}=\mathbbm{1}$.
\begin{equation}
	\begin{split}
	\bra{f}U^{(2)}(t,t_0)\ket{i}=-\bra{f}\int_{t_0}^{t}dt_1\tilde{V}(t_1)\mathbbm{1}\int_{t_0}^{t_1}dt_2\tilde{V}(t_2)\ket{i}=\\-\int_{t_0}^{t}dt_1 e^{i(\omega_f-\omega_j)t_1}\bra{f}V(t_1)\ket{j}\int_{t_0}^{t_1}dt_2e^{i(\omega_j-\omega_i)t_2}\bra{j}V(t_2)\ket{i}
	\end{split}
\end{equation}
Go over the long-time limit $t\rightarrow\infty$ in the final integral and collect the terms belongings to the same delta functions. This gives
\begin{equation}
	\begin{split}
	\bra{f}U^{(2)}(\infty)\ket{i}=\\\frac{\pi i\Omega^2}{2}\bigg[\delta(\omega_f-\omega_i+2\omega_d)\sum_j\frac{\bra{f}b\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
	\delta(\omega_f-\omega_i)\bigg(\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
	\sum_j\frac{\bra{f}b\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg)+\\
	\delta(\omega_f-\omega_i-2\omega_d)\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg]
	\end{split}
\end{equation}
The probability of two-photon transition from state $\ket{i}$ to state $\ket{f}$ is simply the square modulus of the corresponding amplitude. So, $P^{(2)}_{i\rightarrow f}= |	\bra{f}U^{(2)}(\infty)\ket{i}|^2$.
The rate (probability per unit interaction time T) of absorption of $2$ photons is defined as:
\begin{equation}
	W^{(2)}_{i\rightarrow f}=\lim\limits_{T\rightarrow\infty}\frac{P^{(2)}_{i\rightarrow f}}{T}
\end{equation}
For simplifier the equation we have made use of the relation:
\begin{equation}\nonumber
	\delta(\omega_f-\omega_i-2\omega_d) =\frac{1}{2\pi} \lim\limits_{T\rightarrow\infty}\int_{-T/2}^{T/2}e^{i(\omega_f-\omega_i-2\omega_d)t}dt = \lim\limits_{T\rightarrow\infty}\frac{T}{2\pi}
\end{equation} 
For $\omega_f=\omega_i+2\omega_d$.
\begin{equation}\label{prob}
\begin{split}
	W^{(2)}_{i\rightarrow f}=\frac{\pi\Omega^4}{8}\bigg|\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg|^2\delta(\omega_f-\omega_i-2\omega_d)=\\ A^{(2)}_{i\rightarrow f}\delta(\omega_f-\omega_i-2\omega_d)
\end{split}
\end{equation}

@@

\section{Text}

In order to determine which transitions correspond to the lines, the stationary Schrödinger equation was solved \autoref{fig:spectr} in three-level approximation for both of qubits. With the Hamiltonian of the system:
\begin{equation}
	H_{system} = H_{tr1}\otimes \mathbbm{1}+\mathbbm{1}\otimes H_{tr2}+H_{int}
\end{equation}

>>>>

\begin{equation}
A^{(2)}_{1\rightarrow 6} = 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha + \text{$\Omega_1
		$}\right)^2}{\alpha ^{6}\Omega_1^2}
\end{equation}
\begin{equation}
A^{(2)}_{2\rightarrow 5} = 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
		$}\right)^2}{\alpha ^{6}\Omega_1^2}
\end{equation}
From here it follows that in the studied SAM the sideband transitions are prohibited without interaction $(J=0)$ even in the second order, and the avoided crossing we are interested can not be observed.

@@

Solving \autoref{forpsi} by simple iteration gives the series solution
\begin{equation}
	U(t,t_0) = 1+\sum_{n}U^{(n)}(t,t_0)
\end{equation}
\begin{equation}
	U^{(n)}(t,t_0) = -i^n \int_{t_0}^{t}d t_1\tilde{V}(t_1)...\int_{t_0}^{t_{n-1}}d t_n\tilde{V}(t_n)
\end{equation}
For "weak" interaction the series may be truncated to a fine term $n$ and the $n$th- order transition amplitude $\bra{f}U^{(n)}(t,t_0)\ket{i}$ can be evaluated. 
In our case the interaction in interaction picture satisfies the following relation
\begin{equation}
	\begin{split}
	\tilde{V}(t)=\exp(i H_0 t) \Omega\cos(\omega_d t)(\hat b+\hat b^{\dagger})\exp(-i H_0 t)=\\\frac{\Omega}{2} \exp(i H_0 t) \hat{B}(e^{-i\omega_d t}+e^{i\omega_d t})\exp(-i H_0 t)
	\end{split}
\end{equation}
Where, $\hat{b}^{\dagger}+\hat{b}=\hat{B}$.
Taking the matrix element between the initial and the final states $\ket{i}$ and $\ket{f}$, one immediately obtains
\begin{equation}
	\begin{split}
	\bra{f}U^{(1)}(t,t_0)\ket{i}=-i\int_{t_0}^{t}dt_1\tilde{V}(t_1)=\\-i\frac{\Omega}{2}\big[\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i-\omega_d)t_1}\bra{f}\hat{B}\ket{i}+\\
	\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i+\omega_d)t_1}\bra{f}\hat{B}\ket{i}\big]
	\end{split}
\end{equation}
To calculate second-order term we used the following expression $\sum_{j}\ket{j}\bra{j}=\mathbbm{1}$.
\begin{equation}
	\begin{split}
	\bra{f}U^{(2)}(t,t_0)\ket{i}=-\bra{f}\int_{t_0}^{t}dt_1\tilde{V}(t_1)\mathbbm{1}\int_{t_0}^{t_1}dt_2\tilde{V}(t_2)\ket{i}=\\-\int_{t_0}^{t}dt_1 e^{i(\omega_f-\omega_j)t_1}\bra{f}V(t_1)\ket{j}\int_{t_0}^{t_1}dt_2e^{i(\omega_j-\omega_i)t_2}\bra{j}V(t_2)\ket{i}
	\end{split}
\end{equation}
Go over the long-time limit $t\rightarrow\infty$ in the final integral and collect the terms belongings to the same delta functions. This gives
\begin{equation}
	\begin{split}
	\bra{f}U^{(2)}(\infty)\ket{i}=\\\frac{\pi i\Omega^2}{2}\bigg[\delta(\omega_f-\omega_i+2\omega_d)\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
	\delta(\omega_f-\omega_i)\bigg(\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
	\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg)+\\
	\delta(\omega_f-\omega_i-2\omega_d)\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg]
	\end{split}
\end{equation}
The probability of two-photon transition from state $\ket{i}$ to state $\ket{f}$ is simply the square modulus of the corresponding amplitude. So, $P^{(2)}_{i\rightarrow f}= |	\bra{f}U^{(2)}(\infty)\ket{i}|^2$.
The rate (probability per unit interaction time T) of absorption of $2$ photons is defined as:
\begin{equation}
	W^{(2)}_{i\rightarrow f}=\lim\limits_{T\rightarrow\infty}\frac{P^{(2)}_{i\rightarrow f}}{T}
\end{equation}
For simplifier the equation we have made use of the relation:
\begin{equation}\nonumber
	\delta(\omega_f-\omega_i-2\omega_d) =\frac{1}{2\pi} \lim\limits_{T\rightarrow\infty}\int_{-T/2}^{T/2}e^{i(\omega_f-\omega_i-2\omega_d)t}dt = \lim\limits_{T\rightarrow\infty}\frac{T}{2\pi}
\end{equation} 
For $\omega_f=\omega_i+2\omega_d$.
\begin{equation}\label{prob}
\begin{split}
	W^{(2)}_{i\rightarrow f}=\frac{\pi\Omega^4}{8}\bigg|\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg|^2\delta(\omega_f-\omega_i-2\omega_d)=\\ A^{(2)}_{i\rightarrow f}\delta(\omega_f-\omega_i-2\omega_d)
\end{split}
\end{equation}

@@
